Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
modifs referee first paper + BC18 second paper

The non-kissing complex is a simplicial complex of pairwise non-kissing paths in a fixed shape of a grid.
It was introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary shapes.
This complex is known to be a simplicial sphere, and it was actually realized as a polytope using successive edge stellations and suspensions in~\cite[Sect.~4]{McConville}.
Moreover, the dual graph of the non-kissing complex has a natural orientation which equips its facets with a lattice structure~\cite[Thm. 1.1, Sect.~5--8]{McConville}.
Further lattice theoretic and geometric aspects of this complex were recently developed by A.~Garver and T.~McConville in~\cite{GarverMcConville-grid}.

@@

A \defn{path} in~$Q$ is a sequence~$\pi = \alpha_1 \dots \alpha_\ell$ of~$Q_1$ such that~$t(\alpha_k) = s(\alpha_{k+1})$ for all~${k \in [\ell-1]}$ (note that we compose arrows from left to right).
Its \defn{source} (resp.~\defn{target}) is~$s(\pi) \eqdef s(\alpha_1)$ (resp.~$t(\pi) \eqdef t(\alpha_\ell)$), and its \defn{length} is~$\ell(\pi) \eqdef \ell$.
Note that for each vertex~$v \in Q_0$, we also consider the \defn{path~$\varepsilon_v$ of length zero} with source and target~$s(\varepsilon_v) = t(\varepsilon_v) = v$.

@@

For a quiver~$Q = (Q_0, Q_1, s, t)$, define its \defn{reversed quiver}~$\reversed{Q} \eqdef (Q_0, Q_1, t, s)$.
For a path~$\pi$ on~$Q$, define its \defn{reversed path} on~$\reversed{Q}$ by~$\reversed{(\alpha_1 \cdots \alpha_\ell)} = \alpha_\ell \cdots \alpha_1$, and extend it by linearity to a morphism~$kQ \to k\reversed{Q}$ of path algebras.
The \defn{reversed bound quiver} of a bound quiver~$\bar Q = (Q,I)$ is the bound quiver~$\reversed{\bar Q} \eqdef (\reversed{Q},\reversed{I})$.

@@

\begin{theorem}[{\cite[p.\,161]{ButlerRingel}}]
Assume that~$k$ is algebraically closed and consider a string algebra~$A$.
Then the string and band modules over~$A$ form a complete list of indecomposable $A$-modules, up to isomorphism.
Moreover,
  \begin{itemize}
    \item A string module is never isomorphic to a band module.
    \item Two string modules~$M(\rho), M(\rho')$ are isomorphic if and only if~${\rho' = \rho^{\pm 1}}$.
    \item Two band modules~$M(\varpi,\lambda, d)$ and~$M(\varpi', \lambda', d')$ are isomorphic if and only if~$d=d'$, and  
       \begin{itemize}
         \item either $\varpi$ is cyclically equivalent to~$\varpi'$, and~$\lambda = \lambda'$,
         \item or~$\varpi^{-1}$ is cyclically equivalent to~$\varpi'$, and~$\lambda^{-1} = \lambda'$.
       \end{itemize}
  \end{itemize}
\end{theorem}

@@

\begin{definition}
\label{def:peaksDeeps}
We say that a string~$\rho$
  \begin{itemize}
    \item \defn{starts} (resp.~\defn{ends}) \defn{on a peak} if there is no arrow~$\alpha$ such that~$\alpha \rho$ (resp.\,$\rho\alpha^{-1}$) is a string,
    \item \defn{starts} (resp.~\defn{ends}) \defn{in a deep} if there is no arrow~$\alpha$ such that~$\alpha^{-1} \rho$ (resp.~$\rho \alpha$) is a string.
  \end{itemize}
\end{definition}

@@

\begin{example}
The string~$\rho = \gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta$ of Example~\ref{exm:drawingString} in the quiver of Example~\ref{exm:aStringAlgebra} does not start on a deep, and we have
\[
\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString1}}}
\hspace{1.3cm}
_c\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString2}}}
\]
Still in the same quiver of Example~\ref{exm:aStringAlgebra}, the string~$\rho = \delta$ does not start on a peak, and we have
\[
\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString3}}}
\hspace{1.3cm}
_h\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString4}}}
\]
\end{example}

@@

    \item Dually, if~$\rho$ ends on a peak and is not the inverse of a path in~$\bar Q$, then the string obtained by \defn{removing a cohook at the end of~$\rho$} is~${\rho_{c^{-1}} \! \eqdef (_{c^{-1}} \! (\rho^{-1}) )^{-1}}$.

@@

\begin{theorem}[\cite{ButlerRingel}]
\label{theorem: tau for strings}
Consider a string algebra~$A = kQ/I$.
Then the Auslander-Reiten translation transforms string modules to string modules: for a string~$\rho$ of~$\bar Q$, we have~${\tau \big( M(\rho) \big) = M(\rho')}$, where the string~$\rho'$ is obtained by following the table below.
\\[.3cm]
	\centerline{
	\begin{tabular}{|c|c|c|} 
      \hline 
      & $\rho$ does not start in a deep & $\rho$ starts in a deep \\
      \hline
      $\rho$ does not end in a deep & $\rho' = {}_c\rho_c$ & $\rho' = {}_{h^{-1}}(\rho_c)$ \\
      \hline
      $\rho$ ends in a deep & $\rho' = (_c\rho)_{h^{-1}}$ & $\rho' = {}_{h^{-1}}\rho_{h^{-1}}$ \\
      \hline
    \end{tabular}
    }
\\[.3cm]
Dually, we have~$\tau^{-1} \big( M(\rho) \big) = M(\rho'')$, where~$\rho''$ is the string given in the table below.
\\[.3cm]
	\centerline{
    \begin{tabular}{|c|c|c|} 
      \hline 
      & $\rho$ does not start on a peak & $\rho$ starts on a peak \\
      \hline
      $\rho$ does not end on a peak & $\rho'' = {}_h\rho_h$ & $\rho'' = {}_{c^{-1}}(\rho_h)$ \\
      \hline
      $\rho$ ends on a peak & $\rho'' = (_h\rho)_{c^{-1}}$ & $\rho'' = {}_{c^{-1}}\rho_{c^{-1}}$ \\
      \hline
    \end{tabular}
	}
\\[.3cm]
Finally, both the Auslander-Reiten translation~$\tau$ and its inverse~$\tau^{-1}$ preserve the band modules: for a band~$\varpi$ of~$\bar Q$, we have~$\tau \big( M(\varpi, \lambda, d) \big) = M(\varpi, \lambda, d)$ and $\tau^{-1} \big( M(\varpi, \lambda, d) \big)=M(\varpi, \lambda, d)$.
\end{theorem}

@@

\begin{remark}
 A more practical way to think of $\b{g}$-vectors is by noting that $K_0(\proj \bar Q)$ is isomorphic to the free abelian group
 $\bigoplus_{v\in Q_0} \Z [P(v)] \cong \Z^{Q_0}$.  Thus, in the notation of Definition \ref{definition: g-vector of representation},
 if $P_0^M = \bigoplus_{v\in Q_0} \! P(v)^{\oplus a_v}$ and $P_1^M = \bigoplus_{v\in Q_0} \! P(v)^{\oplus b_v}$, 
 then
 \[
  \b{g}(M) = (a_v - b_v)_{v\in Q_0} \in \Z^{Q_0}.
 \] 
 Moreover, if $P = \bigoplus_{v\in Q_0}P(v)^{\oplus n_v}$, then $\b{g}(P[1]) = (-n_v)_{v\in Q_0}$.
\end{remark}

@@

\begin{corollary}
 The $\b{g}$-vector of a string module $M(\rho)$ is $\b{g}(M) = \b{a} - \b{b} - \b{r}$, where
 \begin{itemize}
  \item $\b{a} = (a_v)_{v\in Q_0}$, where $a_v$ is the number of times the vertex $v$ is found at the top of $\rho$;
  \item $\b{b} = (b_v)_{v\in Q_0}$, where $b_v$ is the number of times the vertex $v$ is found at the bottom of $\rho$,
        but not at its start or end;
        \medskip
  \item 
  		\(
         \b{r} = \! \begin{cases}
                   0 & \textrm{if $\rho$ starts and ends in a deep,} \\
                   \b{e}_{t(\alpha)}   & \textrm{if $\rho$ ends in a deep and $\alpha^{-1}\rho$ is a string with $\alpha\in Q_1$,} \\
                   \b{e}_{t(\beta)}    & \textrm{if $\rho$ starts in a deep and $\rho\beta$ is a string, with $\beta\in Q_1$,} \\
                   \b{e}_{t(\alpha)} + \b{e}_{t(\beta)} \!\!\! & \textrm{if $\alpha^{-1}\rho\beta$ is a string, with $\alpha, \beta\in Q_1$,}
                  \end{cases}
        \) \\
        \medskip
        where $(\b{e}_v)_{v \in Q_0}$ is the standard basis of~$\Z^{Q_0}$.
 \end{itemize}
\end{corollary}

@@

Assume first that~$\rho$ attracts~$\rho'$ (Figure~\ref{fig:rho attracts rho'}), and let~$\alpha$ be as in Definition~\ref{definition: dance and attract}.
As~$\rho'$ does not start in a deep,~$\rho''$ starts at a substring~$\alpha_1\cdots\alpha_r$, where~$\alpha_r\cdots\alpha_1\alpha^{-1}$ is the cohook at the start of~$\rho'$.
Let~$0\leq k\leq r$ be maximal such that~$\alpha_k\cdots\alpha_1$ is a substring (possibly a vertex if $k=0$) of~$\rho$ ending in~$u$, where~$u$ is as in Definition~\ref{definition: dance and attract}.
By definition of a cohook,~$\alpha_k\cdots\alpha_1$ has to be on top of~$\rho$, and is at the bottom of~$\rho''$.
By Proposition~\ref{prop:morphismsStringModules}, this implies the existence of a non-zero morphism from~$M(\rho)$ to~$M(\rho'') = \tau M(\rho')$.

>>>>

The non-kissing complex is the simplicial complex of a compatibility relation, called non-kissing, on paths in a fixed shape of a grid.
It was introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary shapes.
This complex is known to be a simplicial sphere, and it was actually realized as a polytope using successive edge stellations and suspensions in~\cite[Sect.~4]{McConville}.
Moreover, the dual graph of the non-kissing complex has a natural orientation which equips its facets with a lattice structure~\cite[Thm. 1.1, Sect.~5--8]{McConville}.
Further lattice theoretic and geometric aspects of this complex were recently developed by A.~Garver and T.~McConville in~\cite{GarverMcConville-grid}.

@@

A \defn{path} in~$Q$ is a sequence~$\pi = \alpha_1 \dots \alpha_\ell$ of~$Q_1$ such that~$t(\alpha_k) = s(\alpha_{k+1})$ for all~${k \in [\ell-1]}$ (note that we compose arrows from left to right).
The \defn{source} (resp.~\defn{target}) of~$\pi$ is~$s(\pi) \eqdef s(\alpha_1)$ (resp.~$t(\pi) \eqdef t(\alpha_\ell)$), and the \defn{length} of~$\pi$ is~$\ell(\pi) \eqdef \ell$.
Note that for each vertex~$v \in Q_0$, we also consider the \defn{path~$\varepsilon_v$ of length zero} with source and target~$s(\varepsilon_v) = t(\varepsilon_v) = v$.

@@

For a quiver~$Q = (Q_0, Q_1, s, t)$, define its \defn{reversed quiver} by~$\reversed{Q} \eqdef (Q_0, Q_1, t, s)$.
For a path~$\pi$ on~$Q$, define its \defn{reversed path} on~$\reversed{Q}$ by~$\reversed{(\alpha_1 \cdots \alpha_\ell)} = \alpha_\ell \cdots \alpha_1$, and extend it by linearity to a morphism~$kQ \to k\reversed{Q}$ of path algebras.
We denote by~$\reversed{I}$ the direct image of~$I$ under this morphism.
The \defn{reversed bound quiver} of a bound quiver~$\bar Q = (Q,I)$ is the bound quiver~$\reversed{\bar Q} \eqdef (\reversed{Q},\reversed{I})$.

@@

\begin{theorem}[{\cite[p.\,161]{ButlerRingel}}]
Assume that~$k$ is algebraically closed and consider a string algebra~$A$.
Then the string and band modules over~$A$ form a complete list of indecomposable $A$-modules, up to isomorphism.
Moreover,
  \begin{itemize}
    \item A string module is never isomorphic to a band module.
    \item Two string modules~$M(\rho)$ and~$M(\rho')$ are isomorphic if and only if~${\rho' = \rho^{\pm 1}}$.
    \item Two band modules~$M(\varpi,\lambda, d)$ and~$M(\varpi', \lambda', d')$ are isomorphic if and only if~$d=d'$, and  
       \begin{itemize}
         \item either $\varpi$ is cyclically equivalent to~$\varpi'$, and~$\lambda = \lambda'$,
         \item or~$\varpi^{-1}$ is cyclically equivalent to~$\varpi'$, and~$\lambda^{-1} = \lambda'$.
       \end{itemize}
  \end{itemize}
\end{theorem}

@@

\begin{definition}
\label{def:peaksDeeps}
We say that a string~$\rho$
  \begin{itemize}
    \item \defn{starts} (resp.~\defn{ends}) \defn{on a peak} if there is no arrow~$\alpha$ such that~$\alpha \rho$ (resp.~$\rho\alpha^{-1}$) is a string,
    \item \defn{starts} (resp.~\defn{ends}) \defn{in a deep} if there is no arrow~$\alpha$ such that~$\alpha^{-1} \rho$ (resp.~$\rho \alpha$) is a string.
  \end{itemize}
\end{definition}

@@

\begin{example}
In the quiver of Example~\ref{exm:aStringAlgebra}, the string~$\rho = \gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta$ of Example~\ref{exm:drawingString} does not start on a deep, and we have
\[
\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString1}}}
\hspace{1.3cm}
_c\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString2}}}
\]
Still in the same quiver of Example~\ref{exm:aStringAlgebra}, the string~$\rho = \delta$ does not start on a peak, and we have
\[
\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString3}}}
\hspace{1.3cm}
_h\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString4}}}
\]
\end{example}

@@

    \item Dually, if~$\rho$ ends on a peak and is not the inverse of a path in~$\bar Q$, then the string obtained by \defn{removing a cohook at the end of~$\rho$} is~${\rho_{c^{-1}} \eqdef (_{c^{-1}} (\rho^{-1}) )^{-1}}$.

@@

\begin{theorem}[\cite{ButlerRingel}]
\label{theorem: tau for strings}
Consider a string algebra~$A = kQ/I$.
The Auslander-Reiten translation transforms string modules to string modules: for a string~$\rho$ of~$\bar Q$, we have~${\tau \big( M(\rho) \big) = M(\rho')}$, where the string~$\rho'$ is obtained by following the table below.
\\[.3cm]
	\centerline{
	\begin{tabular}{|c|c|c|} 
      \hline 
      & $\rho$ does not start in a deep & $\rho$ starts in a deep \\
      \hline
      $\rho$ does not end in a deep & $\rho' = {}_c\rho_c$ & $\rho' = {}_{h^{-1}}(\rho_c)$ \\
      \hline
      $\rho$ ends in a deep & $\rho' = (_c\rho)_{h^{-1}}$ & $\rho' = {}_{h^{-1}}\rho_{h^{-1}}$ \\
      \hline
    \end{tabular}
    }
\\[.3cm]
Dually, we have~$\tau^{-1} \big( M(\rho) \big) = M(\rho'')$, where~$\rho''$ is the string given in the table below.
\\[.3cm]
	\centerline{
    \begin{tabular}{|c|c|c|} 
      \hline 
      & $\rho$ does not start on a peak & $\rho$ starts on a peak \\
      \hline
      $\rho$ does not end on a peak & $\rho'' = {}_h\rho_h$ & $\rho'' = {}_{c^{-1}}(\rho_h)$ \\
      \hline
      $\rho$ ends on a peak & $\rho'' = (_h\rho)_{c^{-1}}$ & $\rho'' = {}_{c^{-1}}\rho_{c^{-1}}$ \\
      \hline
    \end{tabular}
	}
\\[.3cm]
Finally, both the Auslander-Reiten translation~$\tau$ and its inverse~$\tau^{-1}$ preserve the band modules: for a band~$\varpi$ of~$\bar Q$, we have~$\tau \big( M(\varpi, \lambda, d) \big) = M(\varpi, \lambda, d)$ and $\tau^{-1} \big( M(\varpi, \lambda, d) \big)=M(\varpi, \lambda, d)$.
\end{theorem}

@@

\begin{remark}
 A more practical way to think of $\b{g}$-vectors is by noting that $K_0(\proj \bar Q)$ is isomorphic to the free abelian group
 $\bigoplus_{v\in Q_0} \Z [P(v)] \cong \Z^{Q_0}$.  Thus, in the notation of Definition \ref{definition: g-vector of representation},
 if $P_0^M = \bigoplus_{v\in Q_0}P(v)^{\oplus a_v}$ and $P_1^M = \bigoplus_{v\in Q_0}P(v)^{\oplus b_v}$, 
 then
 \[
  \b{g}(M) = (a_v - b_v)_{v\in Q_0} \in \Z^{Q_0}.
 \] 
 Moreover, if $P = \bigoplus_{v\in Q_0}P(v)^{\oplus n_v}$, then $\b{g}(P[1]) = (-n_v)_{v\in Q_0}$.
\end{remark}

@@

\begin{corollary}
 The $\b{g}$-vector of a string module $M(\rho)$ is $\b{g}(M) = \b{a} - \b{b} - \b{r}$, where
 \begin{itemize}
  \item $\b{a} = (a_v)_{v\in Q_0}$, where $a_v$ is the number of times the vertex $v$ is found at the top of $\rho$;
  \item $\b{b} = (b_v)_{v\in Q_0}$, where $b_v$ is the number of times the vertex $v$ is found at the bottom of $\rho$,
        but not at its start or end;
        \medskip
  \item 
  		\(
         \b{r} = \begin{cases}
                   0 & \textrm{if $\rho$ starts and ends in a deep,} \\
                   \b{e}_{t(\alpha)}   & \textrm{if $\rho$ ends in a deep and $\alpha^{-1}\rho$ is a string, with $\alpha\in Q_1$,} \\
                   \b{e}_{t(\beta)}    & \textrm{if $\rho$ starts in a deep and $\rho\beta$ is a string, with $\beta\in Q_1$,} \\
                   \b{e}_{t(\alpha)} + \b{e}_{t(\beta)}  & \textrm{if $\alpha^{-1}\rho\beta$ is a string, with $\alpha, \beta\in Q_1$,}
                  \end{cases}
        \) \\
        \medskip
        where $(\b{e}_v)_{v \in Q_0}$ is the standard basis of~$\Z^{Q_0}$.
 \end{itemize}
\end{corollary}

@@

Assume first that~$\rho$ attracts~$\rho'$ (Figure~\ref{fig:rho attracts rho'}), and let~$\alpha$ be as in Definition~\ref{definition: dance and attract}.
Since~$\rho'$ does not start in a deep,~$\rho''$ starts at a substring~$\alpha_1\cdots\alpha_r$, where~$\alpha_r\cdots\alpha_1\alpha^{-1}$ is the cohook at the start of~$\rho'$.
Let~$0\leq k\leq r$ be maximal such that~$\alpha_k\cdots\alpha_1$ is a substring (possibly a vertex if $k=0$) of~$\rho$ ending in~$u$, where~$u$ is as in Definition~\ref{definition: dance and attract}.
By definition of a cohook,~$\alpha_k\cdots\alpha_1$ has to be on top of~$\rho$, and is at the bottom of~$\rho''$.
By Proposition~\ref{prop:morphismsStringModules}, this implies the existence of a non-zero morphism from~$M(\rho)$ to~$M(\rho'') = \tau M(\rho')$.

### 2018-07-13 secondPaper/accordionComplexSurfaces.tex
minor modifs
generaliZing
modifs referee first paper + BC18 second paper

\begin{abstract}
Starting from a locally gentle bound quiver, we define on the one hand a simplicial complex, called the non-kissing complex.
On the other hand, we construct a punctured, marked, oriented surface with boundary, endowed with a pair of dual dissections.
From those geometric data, we define two simplicial complexes: the accordion complex, and the slalom complex, generalising work of A. Garver and T. McConville in the case of a disk.
We show that all three simplicial complexes are isomorphic, and that they are pure and thin.
In particular, there is a notion of mutation on their facets, akin to $\tau$-tilting mutation.
Along the way, we also construct inverse bijections between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of punctured, marked, oriented surfaces with boundary, endowed with a pair of dual dissections.
\end{abstract}

@@

The idea of associating a finite-dimensional algebra to a dissection (or a triangulation) of a surface seems to take its roots in the theory of cluster algebras and cluster categories.
This was first done for triangulations of polygons in \cite{CalderoChapotonSchiffler}, and then for any orientable surface with boundary in \cite{ABCP, Labardini}.  
The algebra of a dissection as we shall use it in this paper has appeared in \cite{DavidRoeslerSchiffler}.
In most of the above cases, the algebras obtained are gentle algebras.
It has also been shown in \cite{BaurSimoes} that any gentle algebra is obtained from a dissection of a surface, and that the module category of the algebra can be interpreted by using curves on the surface.
In the case where the surface is a polygon, the $\tau$-tilting theory of the algebra of a dissection has been studied in \cite{PaluPilaudPlamondon, PilaudPlamondonStella}.

Conversely, the construction of a surface associated to a gentle algebra has appeared in \cite{OpperPlamondonSchroll}.
We give a different construction of the same surface in this paper, which is obtained by ``glueing'' quadrilaterals to the arrows of the blossoming quiver (as defined in \cite{PaluPilaudPlamondon}, and called ``framed quiver'' in \cite{BrustleDouvilleMousavandThomasYildirim}).
Our construction has the advantage that it easily yields the two dual dissections of the surface at the same time (the dissection and dual lamination of \cite{OpperPlamondonSchroll}).
We note that our dissections are always cellular, while those found in \cite{BaurSimoes} can be arbitrary.
Remarkably, gentle algebras and surfaces were linked recently in \cite{HaidenKatzarkovKontsevich}, where the Fukaya category of the surface is shown to be equivalent to the bounded derived category of the associated gentle algebra.

@@

The following definition generalises the one from \cite{MannevillePilaud-accordion} for the case where~$\bar \surface$ is a disk.  A very similar definition appears in \cite{BaurSimoes} in a slightly different context under the name ``permissible~arc''.

@@

\begin{lemma}
\label{lemm:quiverOfDissectionIsLocallyGentle}
The bound quiver~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a locally gentle bound quiver.
\end{lemma}
\begin{proof}
Each edge~$a$ of~$\dissection$ has two endpoints, and at each endpoint there is at most one edge of~$\dissection$ coming immediately after~$a$ in the clockwise order, and at most one edge of~$\dissection$ coming immediately before~$a$.
Thus, in~$Q_{\dissection}$, there are at most two arrows leaving~$a$ and at most two arriving in~$a$.
Among these arrows, those arising from the same endpoint of~$a$ will be composable, and those arising from different endpoints will yield relations.
Thus $\bar Q_{\dissection}$ is locally gentle.
\end{proof}

@@

\begin{proposition}
\label{prop:dissectionsAreCellular}
Let~$\bar Q$ be a locally gentle bound quiver.
Then the dissections~$\dissection_{\bar Q}$ and~$\dissection\dual\!\!_{\bar Q}$ are cellular and dual to each other.
\end{proposition}
\begin{proof}
In the construction of~$\surface_{\bar Q}$, if two arrows~$\alpha$ and~$\beta$ of~$\bar Q \blossom$ are such that~${t(\alpha) = s(\beta)}$ and~${\alpha\beta \in I\blossom}$, then the vertices~$v(\alpha)$ and~$v(\beta)$ are identified on the surface.
Thus, any two arrows of a given path contribute the same vertex of~$V_{\bar Q}$, so~$V_{\bar Q}$ is in bijection with the set of maximal paths in~$\bar Q\blossom$.

@@

\begin{theorem}
\label{thm:complexesCoincide}
The non-kissing and non-crossing complexes are isomorphic:
\begin{itemize}
\item for any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$,
\item for any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.

\end{itemize}
\end{theorem}

@@

\begin{lemma}
\label{lemm:countercurrentOrderIsTotal}
For any face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the countercurrent order~$\prec_\alpha$ defines a total order on~$F_{\alpha}$.
\end{lemma}
\begin{proof}
 The proof of \cite[Lem.~2.21]{PaluPilaudPlamondon} applies here.
\end{proof}

\begin{lemma}
\label{lemm:facesHaveMaximalElement}
For any finite non-kissing face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the set~$F_\alpha$ is either empty or admits a maximal element for the countercurrent order~$\prec_\alpha$.
\end{lemma}
\begin{proof}
 We provide two proofs of the lemma.  One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$, using the isomorphism of Theorem \ref{thm:complexesCoincide} and Remark \ref{rem:countercurrentOrderOnSurface}.

>>>>

\begin{abstract}
Starting from a locally gentle bound quiver, we define on the one hand a simplicial complex, called the non-kissing complex.
On the other hand, we construct a punctured, marked, oriented surface with boundary, endowed with a pair of dual dissections.
From those geometric data, we define two simplicial complexes: the accordion complex, and the slalom complex, generalizing work of A. Garver and T. McConville in the case of a disk.
We show that all three simplicial complexes are isomorphic, and that they are pure and thin.
In particular, there is a notion of mutation on their facets, akin to $\tau$-tilting mutation.
Along the way, we also construct inverse bijections between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of punctured, marked, oriented surfaces with boundary, endowed with a pair of dual dissections.
\end{abstract}

@@

The idea of associating a finite-dimensional algebra to a dissection (or a triangulation) of a surface seems to take its roots in the theory of cluster algebras and cluster categories.
This was first done for triangulations of polygons in \cite{CalderoChapotonSchiffler}, and then for any orientable surface with boundary in \cite{ABCP, Labardini}.  
The algebra of a dissection as we shall use it in this paper has appeared in \cite{DavidRoeslerSchiffler}.
In most of the above cases, the algebras obtained are gentle algebras.
It has also been shown in \cite{BaurCoelhoSimoes} that any gentle algebra is obtained from a dissection of a surface, and that the module category of the algebra can be interpreted by using curves on the surface.
In the case where the surface is a polygon, the $\tau$-tilting theory of the algebra of a dissection has been studied in \cite{PaluPilaudPlamondon, PilaudPlamondonStella}.

Conversely, the construction of a surface associated to a gentle algebra has appeared in \cite{OpperPlamondonSchroll}.
We give a different construction of the same surface in this paper, which is obtained by ``glueing'' quadrilaterals to the arrows of the blossoming quiver (as defined in \cite{PaluPilaudPlamondon}, and called ``framed quiver'' in \cite{BrustleDouvilleMousavandThomasYildirim}).
Our construction has the advantage that it easily yields the two dual dissections of the surface at the same time (the dissection and dual lamination of \cite{OpperPlamondonSchroll}).
We note that our dissections are always cellular, while those found in \cite{BaurCoelhoSimoes} can be arbitrary.
Remarkably, gentle algebras and surfaces were linked recently in \cite{HaidenKatzarkovKontsevich}, where the Fukaya category of the surface is shown to be equivalent to the bounded derived category of the associated gentle algebra.

@@

The following definition generalises the one from \cite{MannevillePilaud-accordion} for the case where~$\bar \surface$ is a disk.  A very similar definition appears in \cite{BaurCoelhoSimoes} in a slightly different context under the name ``permissible~arc''.

@@

\begin{lemma}
\label{lemm:quiverOfDissectionIsLocallyGentle}
The bound quiver~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a locally gentle bound quiver.
\end{lemma}

\begin{proof}
Each edge~$a$ of~$\dissection$ has two endpoints, and at each endpoint there is at most one edge of~$\dissection$ coming immediately after~$a$ in the clockwise order, and at most one edge of~$\dissection$ coming immediately before~$a$.
Thus, in~$Q_{\dissection}$, there are at most two arrows leaving~$a$ and at most two arriving in~$a$.
Among these arrows, those arising from the same endpoint of~$a$ will be composable, and those arising from different endpoints will yield relations.
Thus $\bar Q_{\dissection}$ is locally gentle.
\end{proof}

@@

\begin{proposition}
\label{prop:dissectionsAreCellular}
Let~$\bar Q$ be a locally gentle bound quiver.
Then the dissections~$\dissection_{\bar Q}$ and~$\dissection\dual\!\!_{\bar Q}$ are cellular and dual to each other.
\end{proposition}

\begin{proof}
In the construction of~$\surface_{\bar Q}$, if two arrows~$\alpha$ and~$\beta$ of~$\bar Q \blossom$ are such that~${t(\alpha) = s(\beta)}$ and~${\alpha\beta \in I\blossom}$, then the vertices~$v(\alpha)$ and~$v(\beta)$ are identified on the surface.
Thus, any two arrows of a given path contribute the same vertex of~$V_{\bar Q}$, so~$V_{\bar Q}$ is in bijection with the set of maximal paths in~$\bar Q\blossom$.

@@

\begin{theorem}
\label{thm:complexesCoincide}
The non-kissing and non-crossing complexes are isomorphic:
\begin{itemize}
\item for any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$,
\item for any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
\end{itemize}
\end{theorem}

@@

\begin{lemma}
\label{lemm:countercurrentOrderIsTotal}
For any face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the countercurrent order~$\prec_\alpha$ defines a total order on~$F_{\alpha}$.
\end{lemma}

\begin{proof}
The proof of \cite[Lem.~2.21]{PaluPilaudPlamondon} applies here.
\end{proof}

\begin{lemma}
\label{lemm:facesHaveMaximalElement}
For any finite non-kissing face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the set~$F_\alpha$ is either empty or admits a maximal element for the countercurrent order~$\prec_\alpha$.
\end{lemma}

\begin{proof}
We provide two proofs of the lemma.  One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$, using the isomorphism of Theorem \ref{thm:complexesCoincide} and Remark \ref{rem:countercurrentOrderOnSurface}.
